% !TEX root = ../preamble.tex

\section{Test runs of similarity search}
These are the results of 5 test runs using threshold \textit{0.6} \\ \\
Run 1, threshold = 0.6 \\
Return 1 movie: \\
Movies "Avril" and "Coster Bill" have jaccard similarity: 0.64. \\\\
Run 2, 3, 4 and 5, threshold = 0.6 \\
Return 0 movies. \\

Because of the low amount of results we, temporarily lowered the threshold to \textit{0.4} and made 5 new test runs: \\ \\
Run 1, threshold = 0.4 \\
Return 2 movies: \\
Movies "Brittany’s Foot Tease" and "Buuel" have jaccard similarity: 0.5. \\
Movies "38" and "Bruce Springsteen \& the E Street Band: Live in Barcelona" have jaccard similarity: 0.44. \\ \\
Run 2 \\
Movies "All I Desire" and "Apartment for Peggy" have jaccard similarity: 0.6. \\
Movies "Cndida” and "Crcel de Cananea” have jaccard similarity: 0.43. \\ \\
Run 3, threshold = 0.4. \\
Movies "Bodily Harm" and "Castro Laboreiro" have jaccard similarity: 0.43. \\
Movies "Cndida and "Crcel de Cananea” have jaccard similarity: 0.43. \\
Movies "Atta Boy’s Last Race" and "Bodily Harm" have jaccard similarity: 0.42. \\
Movies "Ablution" and "Accadde tra le sbarre" have jaccard similarity: 0.49. \\ \\
Run 4, threshold = 0.4. \\
Movies "Awal el shahir" and "Awal hub" have jaccard similarity: 0.5. \\
Movies "Cndida” and "Crcel de Cananea” have jaccard similarity: 0.43. \\ \\
Run 5, threshold = 0.4. \\
Movies "Avci" and "Cento cavalieri” have jaccard similarity: 0.41. \\
Movies "Apartment for Peggy" and "Chyortova dyuzhyna" have jaccard similarity: 0.42. \\
Movies "After School Special" and "Blond: Eva Blond! - Der Zwerg im Schliefach" have jaccard similarity: 0.47. \\
Movies "Dai nu qing hen" and "Dai Nippon teikoku" have jaccard similarity: 0.44. \\
Movies "Brittany’s Foot Tease" and "Buuel" have jaccard similarity: 0.5. \\
Movies "Avril" and "Coster Bill" have jaccard similarity: 0.64. \\

From the limited amounts of test that we have run, it is clear that quite a few of all the actual movie pairs above the threshold is found at every run. The amount of candidate pairs is extremely wide, with the lowest values being under 1000 and the highest values being above 70000.


